The cardinality-constrained college application problem: The nestedness property and implications for student welfare

### 2022-07-20 paper_alma/abstract.tex
abstract

This paper considers a novel portfolio optimization problem called the college application problem. We show that the objective function is a nondecreasing submodular set function and provide a quadratic-time solution algorithm. We discuss the properties of the optimal solution and their implications for student welfare.

>>>>

This paper considers a novel portfolio optimization problem called the college application problem. We show that the objective function is a nondecreasing submodular set function and provide a quadratic-time solution algorithm for the college application with a cardinality constraint. We discuss the properties of the optimal solution and their implications for student welfare. Our analysis suggests a rational basis for findings in the behavioral science literature on systematic differences in the application styles of low- and high-income students. Our results also help explain the underwhelming effectiveness of nudges designed to encourage low-income students to apply to more colleges.
